Active Learning for SAT Solver Benchmarking

### 2022-10-11 paper/paper.tex
algo2
table1

\begin{table}[tbp]
  \centering
  \begin{tabular}{
    m{0.32\textwidth}
    >{\centering\arraybackslash}m{0.16\textwidth}
    >{\centering\arraybackslash}m{0.16\textwidth}
    >{\centering\arraybackslash}m{0.16\textwidth}
    >{\centering\arraybackslash}m{0.16\textwidth}
  }
    \hline
    Feature & Hoos~\cite{HoosKSS13} & SMAC~\cite{HutterHL11} & Matricon~\cite{MatriconAFSH21} & Our approach \\
    \hline
    Ranking & \cmark & \xmark & \cmark & \cmark \\
    Runtime Minimization & \xmark & \cmark & \cmark & \cmark \\
    % Feature-based & \cmark & \cmark & \cmark & \cmark \\
    Incremental/Non-Random & \xmark & \xmark & \cmark & \cmark \\
    % \tablefootnote{While using a model-based selection strategy to select the next configuration to evaluate, the instance sampling is done randomly.}
    Scoring & \cmark & \xmark & \xmark & \cmark \\
    % \tablefootnote{While they provide a confidence measure, the strategy's output is still only binary, i.e., whether a solver A is better or worse than solver B.}
    Scalability & \cmark & \cmark & \xmark & \cmark \\
    \hline
  \end{tabular}
  ~\\[1em]
  \caption{Support for desired criteria from Section~\ref{sec:intro}.
	The table compares a static benchmark-selection approach~\cite{HoosKSS13}, an algorithm configuration system~\cite{HutterHL11}, an existing active-learning approach~\cite{MatriconAFSH21}, as well as our approach.
  }
  \label{tab:requirements}
\end{table}

@@

    \BlankLine
    $\mathcal{R} \leftarrow \mathcal{R} \cup \bigl\{ (e, t) \bigr\}$
  }
  $s \leftarrow \operatorname{predictScore}(\mathcal{M})$ \tcp*{cf. Section~\ref{sec:main:model}}

  \BlankLine
  \Return $(s, \mathcal{R})$

@@

  %\KwIn{A pool of instances $\mathcal{I}$, a set of solvers $\mathcal{S}$ with known runtimes $r\!: \mathcal{S} \times \mathcal{I} \rightarrow \left[0, \tau\right] \cup \left\lbrace \perp \right\rbrace$, and PAR-2 scores $par2\!: \mathcal{S} \rightarrow \mathbb{R}$ for each solver.}
  \KwIn{Solvers $\mathcal{A}$, Instaces $\mathcal{I}$, Runtimes $r : \mathcal{A} \times \mathcal{I} \rightarrow [0, \tau]$}
  \KwOut{Average ranking accuracy $\bar{O}_{\operatorname{acc}}$, Average fraction of runtime $\bar{O}_{\operatorname{rt}}$}
  \BlankLine

  $res \leftarrow \emptyset$

  \For{$\hat{a} \in \mathcal{A}$}{
    $\mathcal{A}' \leftarrow \mathcal{S} \setminus \left\lbrace \hat{a} \right\rbrace$

    $\left( s, \tilde{\mathcal{I}} \right) \leftarrow \operatorname{runALAlgorithm}\!\left(\mathcal{I}, \mathcal{A}', r, \hat{a}\right)$ \tcp*{Refer to Algorithm~\ref{algALBenchmark}}

    $O_{\operatorname{acc}} \leftarrow \frac{1}{|\mathcal{A}|} \sum\limits_{a \in \mathcal{A}} \left[\operatorname{sign}(s(a) - s(\hat{a})) = \operatorname{sign}(par2(a) - par2(\hat{a})) \right]$

    \tcp*{Iverson-bracket notation}
    %JB: maybe we can simplify the expresson, since readers might be unfamiliar with that notation (I had to look it up)

	$r' \leftarrow \sum\limits_{i \in \tilde{\mathcal{I}}} r(i, \hat{a})$\;
	$r \leftarrow \sum\limits_{i \in \mathcal{I}} r(i, \hat{a})$\;
    $O_{\operatorname{rt}} \leftarrow \frac{r'}{r}$

    $res \leftarrow res \cup \left\lbrace \left( O_{\operatorname{acc}},\, O_{\operatorname{rt}} \right) \right\rbrace$
  }

  $\left( \bar{O}_{\operatorname{acc}},\, \bar{O}_{\operatorname{rt}} \right) \leftarrow \operatorname{mean}\!\left( res \right)$ \;
  \Return $\left( \bar{O}_{\operatorname{acc}},\, \bar{O}_{\operatorname{rt}} \right)$
\end{algorithm}

>>>>

\begin{table}[tbp]
  \centering
  \begin{tabular}{
    m{0.32\textwidth}
    >{\centering\arraybackslash}m{0.16\textwidth}
    >{\centering\arraybackslash}m{0.16\textwidth}
    >{\centering\arraybackslash}m{0.16\textwidth}
    >{\centering\arraybackslash}m{0.16\textwidth}
  }
    \hline
    Feature & Hoos~\cite{HoosKSS13} & SMAC~\cite{HutterHL11} & Matricon~\cite{MatriconAFSH21} & Our approach \\
    \hline
    Ranking & \cmark & \xmark & \cmark & \cmark \\
    Runtime Minimization & \xmark & \cmark & \cmark & \cmark \\
    % Feature-based & \cmark & \cmark & \cmark & \cmark \\
    Incremental/Non-Random & \xmark & \xmark & \cmark & \cmark \\
    % \tablefootnote{While using a model-based selection strategy to select the next configuration to evaluate, the instance sampling is done randomly.}
    Scoring & \cmark & \xmark & \xmark & \cmark \\
    % \tablefootnote{While they provide a confidence measure, the strategy's output is still only binary, i.e., whether a solver A is better or worse than solver B.}
    Scalability & \cmark & \cmark & \xmark & \cmark \\
    \hline
  \end{tabular}
  ~\\[1em]
  \caption{Comparison of features of our benchmark selection approach, the static benchmark-selection approach by Hoos~et~al.~\cite{HoosKSS13}, the algorithm configuration system SMAC~\cite{HutterHL11}, and the active-learning approaches by Matricon et al.~\cite{MatriconAFSH21}.
  }
  \label{tab:requirements}
\end{table}

@@

    \BlankLine
    $\mathcal{R} \leftarrow \mathcal{R} \cup \bigl\{ (e, t) \bigr\}$
  }
  $s_{\hat a} \leftarrow \operatorname{predictScore}(\mathcal{M})$ \tcp*{cf. Section~\ref{sec:main:model}}

  \BlankLine
  \Return $(s_{\hat a}, \mathcal{R})$

@@

  %\KwIn{A pool of instances $\mathcal{I}$, a set of solvers $\mathcal{S}$ with known runtimes $r\!: \mathcal{S} \times \mathcal{I} \rightarrow \left[0, \tau\right] \cup \left\lbrace \perp \right\rbrace$, and PAR-2 scores $par2\!: \mathcal{S} \rightarrow \mathbb{R}$ for each solver.}
  \KwIn{Solvers $\mathcal{A}$, Instaces $\mathcal{I}$, Runtimes $r : \mathcal{A} \times \mathcal{I} \rightarrow [0, \tau]$}
  \KwOut{Average Rank Accuracy $\bar{O}_{\operatorname{acc}}$, Average Fraction of Runtime $\bar{O}_{\operatorname{rt}}$}
  \BlankLine

  $O \leftarrow \emptyset$
  \BlankLine

  \For{$\hat{a} \in \mathcal{A}$}{
    $\mathcal{A}' \leftarrow \mathcal{A} \setminus \left\lbrace \hat{a} \right\rbrace$ \;
    $(s_{\hat a}, \mathcal{R}) \leftarrow \operatorname{runALAlgorithm}(\mathcal{A}', \mathcal{I}, r, \hat{a})$ \tcp*{Refer to Algorithm~\ref{algALBenchmark}}

	\BlankLine
	\tcp{Determine Rank Accuracy}
    $O_{\operatorname{acc}} \leftarrow 0$ \;    
    \For{$a \in \mathcal{A}$}{
    	\If{$\bigl(s_k(a) - s_{\hat a}\bigr) \cdot \bigl(\operatorname{par_2}(a) - \operatorname{par_2}(\hat a)\bigr) > 0$}{
   		    $O_{\operatorname{acc}} \leftarrow O_{\operatorname{acc}} + \frac{1}{|\mathcal{A}|}$ \;
    	}
    }

	\BlankLine
	\tcp{Determine Runtime Fraction}
	$r \leftarrow \sum\limits_{e \in \mathcal{I}} r(\hat a, e)$\;
	$O_{\operatorname{rt}} \leftarrow 0$\;
    \For{$e \in \mathcal{I}$}{
		\If{$\exists t, (e,t) \in \mathcal{R}$}{
			$O_{\operatorname{rt}} \leftarrow O_{\operatorname{rt}} + \frac{t}{r}$\;
		}
	}

	\BlankLine
    $O \leftarrow O \cup \bigl\{ ( O_{\operatorname{acc}},\, O_{\operatorname{rt}} ) \bigr\}$
  }

  \BlankLine
  $\bigl( \bar{O}_{\operatorname{acc}}, \bar{O}_{\operatorname{rt}} \bigr) \leftarrow \operatorname{average}(O)$ \;

  \BlankLine
  \Return $\bigl( \bar{O}_{\operatorname{acc}}, \bar{O}_{\operatorname{rt}} \bigr)$
\end{algorithm}
